Predicting instabilities of a tuneable ring laser with an iterative map model

### 2021-06-05 Papers/Journal/Tuneable_Lasers.tex
Finished edits

@@

@@

% Table of parameter values
\begin{table*}[!b]
	\centering
	\caption{Range of parameter values (taken from~\cite{agrawal2013, burgoyne2014, burgoyneemail, tamura1996, usechak2005}).}
 	\label{tab:values}
 	\begin{tabular}{clll}
		\hline
		Parameter & Description & Value & Units \\
		\hline\noalign{\smallskip}
		$T_M$ & Characteristic modulation time & $15$--$150$ & ps \\
		$\beta_2 L_D$ & Dispersion provided by the CFBG & $10$--$2000$ & ps$^2$ \\
		$\gamma$ & Kerr nonlinearity coefficient & $0.001$--$0.01$ & W$^{-1}$ m$^{-1}$ \\
		$L_f$ & Length of fibre between gain and optical coupler & $0.15$--$1$ & m \\
		$L_g$ & Length of the Er-doped gain fibre & $2$--$3$ & m \\
		$\alpha$ & Loss of fibre due to scattering and absorption & $10^{-4}$--$0.3$ & m$^{-1}$ \\
		$R$ & Reflectivity of optical coupler & $0.1$--$0.9$ & -- \\
		$\Es$ & Saturation energy of Er-doped gain fibre & $10^3$--$10^4$ & pJ \\
		$g_0$ & Small signal gain &  $1$--$10$ & m$^{-1}$ \\
		$L_T$ & Total length of fibre in the cavity & $10$--$100$ & m \\
		\noalign{\smallskip}\hline
	\end{tabular}
\end{table*}

@@

>>>>

\renewcommand{\topfraction}{.75}
\renewcommand{\floatpagefraction}{.8}

@@

% Table of parameter values
\begin{table*}[tbp]
	\centering
	\caption{Range of parameter values (taken from~\cite{agrawal2013, burgoyne2014, burgoyneemail, tamura1996, usechak2005}).}
 	\label{tab:values}
 	\begin{tabular}{clll}
		\hline
		Parameter & Description & Value & Units \\
		\hline\noalign{\smallskip}
		$T_M$ & Characteristic modulation time & $15$--$150$ & ps \\
		$\beta_2 L_D$ & Dispersion provided by the CFBG & $10$--$2000$ & ps$^2$ \\
		$\gamma$ & Kerr nonlinearity coefficient & $0.001$--$0.01$ & W$^{-1}$ m$^{-1}$ \\
		$L_f$ & Length of fibre between gain and optical coupler & $0.15$--$1$ & m \\
		$L_g$ & Length of the Er-doped gain fibre & $2$--$3$ & m \\
		$\alpha$ & Loss of fibre due to scattering and absorption & $10^{-4}$--$0.3$ & m$^{-1}$ \\
		$R$ & Reflectivity of optical coupler & $0.1$--$0.9$ & -- \\
		$\Es$ & Saturation energy of Er-doped gain fibre & $10^3$--$10^4$ & pJ \\
		$g_0$ & Small signal gain &  $1$--$10$ & m$^{-1}$ \\
		$L_T$ & Total length of fibre in the cavity & $10$--$100$ & m \\
		\noalign{\smallskip}\hline
	\end{tabular}
\end{table*}

@@

@@

To further justify the decoupling of the GNSLE into an iterative map, \eqref{eq:nlse} can be written in a dimensionless form where the characteristic time, length, and amplitude are taken to be $T_M$, $L$, and $P_0^{1/2}$, respectively. Letting
\begin{align}
	T &= T_M \widetilde{T}, & z &= L \widetilde{z}, & A &= P_0^{1/2} \widetilde{A},
\end{align}
\eqref{eq:nlse} becomes
\begin{align}
	\pdiff{\widetilde{A}}{\widetilde{z}} = \frac{-i \, \textrm{sgn}(\beta_2) L}{L_\textrm{disp}} \pdiff[2]{\widetilde{A}}{\widetilde{T}} + i \frac{L}{L_\textrm{NL}} |\widetilde{A}|^2 \widetilde{A} + \frac{1}{2}g_0 L \, \widetilde{g}(\widetilde{A}) \widetilde{A} - \alpha L \widetilde{A},
	\label{eq:ndgnlse}
\end{align}
where
\begin{equation}
	\begin{gathered}
		\widetilde{g}(\widetilde{A}) = \left( 1 + \frac{P_0 T_M}{\Es} \int_{-\infty}^\infty |\widetilde{A}|^2 \, \df \widetilde{T} \right)^{-1}, \\
		L_\textrm{disp} = \frac{T_M^2}{|\beta_2|}, \hspace{2cm} L_\textrm{NL} = \frac{1}{\gamma P_0}.
	\end{gathered}
\end{equation}
The dispersion length $L_\textrm{disp}$, and the nonlinear length $L_\textrm{NL}$, are identified in~\cite{agrawal2013} as length scales over which either the dispersive, or nonlinear, effects dominate the evolution of a pulse.

For the gain, the characteristic quantity is $g_0 L$, and within the gain fibre $g_0 L = \bigO{10^1}$. Outside this domain, $g_0 L = \bigO{10^{-3}}$, reflecting the small amount of gain in these other regions. A similar argument can be made for the attenuation factor $-\alpha L$ by considering the output coupler to be analogous to additional length of fibre. The dispersion-dominant regime is characterized by the condition~\cite{agrawal2013}
\begin{align}
	\frac{L_\textrm{disp}}{L_\textrm{NL}} = \frac{\gamma P_0 T_M^2}{|\beta_2|} \ll 1.
\end{align}
This condition is attained in regions with relatively low pulse power, and a large value of $|\beta_2|$. The nonlinearity-dominant regime corresponds to $L_\textrm{disp} / L_\textrm{NL} \gg 1$, with a much larger pulse power, and small value of $|\beta_2|$. For a single-mode silicon fibre $|\beta_2| \sim 20$ ps$^2$/km, illustrating that the effective dispersion, $|\beta_2| L$, varies by a factor of $10^4$ from inside to outside the dispersive~region.

We show in Table \ref{tab:NDparams} an order of magnitude estimate of the size of each of the non-dimensional parameters in \eqref{eq:ndgnlse}. Within each of the four regions we find that one parameter (highlighted) dominates the three others, further justifying the proposed decoupling process.

% Table of relative dynamics
\begin{table}[tbp]
	\centering
	\caption{Relative size of loss, dispersion, gain, and nonlinearity in each section of the cavity.}
 	\label{tab:NDparams}
 	\begin{tabular}{ccccc}
		\hline
		Parameter \hspace*{-1mm} & Loss & Dispersion & Gain & Fibre \\
		\hline\noalign{\smallskip}
		$\alpha L$ & \color{color2}$\bigO{10^{-1}}$ & $\bigO{10^{-3}}$ & $\bigO{10^{-3}}$ & $\bigO{10^{-3}}$ \\
		$L / L_\text{disp}$ & $\bigO{10^{-3}}$ & \color{color2}$\bigO{10^{-1}}$ & $\bigO{10^{-3}}$ & $\bigO{10^{-3}}$ \\
		$g_0 L$ & $\bigO{10^{-4}}$ & $\bigO{10^{-4}}$ & \color{color2}$\bigO{10^{1}}$ & $\bigO{10^{-4}}$ \\
		$L / L_\text{NL}$ & $\bigO{10^{-3}}$ & $\bigO{10^{-3}}$ & $\bigO{10^{-3}}$ & \color{color2}$\bigO{10^{0}}$ \\
		\noalign{\smallskip}\hline
	\end{tabular}
\end{table}
